---
title: "A3: SPL Library Checkouts"
output: html_document
---

### Introduction

An introduction of the data and a description of the trends/books/items you are choosing to analyze (and why!)

### Summary Information

Write a summary paragraph of findings that includes the 5 values calculated from your summary information R script

These will likely be calculated using your DPLYR skills, answering questions such as:

- What is the average number of checkouts for each item?
- What is the month or year with the most/least checkouts for a book that you're interested in?
- What is the month or year with the most/least checkouts for ebooks?
- How has the number of print book checkouts changed over time?

Feel free to calculate and report values that you find relevant.

### The Dataset

Who collected/published the data?

* The Seattle Public Library.

What are the parameters of the data (dates, number of checkouts, kinds of books, etc.)?

* Usage class, checkout type, material Type, checkout date, number of checkouts, book title,
ISBN, book author, book type, publisher, publication year.
There are 12 columns and 2757014 rows.
  
How was the data collected or generated?

* The data was collected by a monthly count of the Seattle Public Library checkouts by book title for physical and digital books from 2022 to 2023.

Why was the data collected?

* The data was collected in order to understand the reading patterns (or trends) of people in Seattle.

What, if any, ethical questions do you need to consider when working with this data? 

* One ethical question would be whether the data is based on people's consent.

What are possible limitations or problems with this data?   (at least 200 words)

* One limitation is that the data is updated monthly, based on the sixth day of the month   with the previous month's data. Since the data is not updated every single day, the time     span of the data collection becomes relatively long, which has the possibility of limiting   the data. If the data is updated daily (though it is a lot of work), the relevant trends     can be shown much more clearly. Another limitation within the data is that the data does not take these books which have no checkouts during the chosen period into consideration. This limitation may make the date less powerful in terms of representing the Seattle Public Library.   

* One problem within the data is that there are a number of missing values in the ISBN column as well as the Creator column. These missing values are likely to reduce the representativeness of the corresponding samples, which might lead to a reduction of the statistical power of the data. Another problem within the data is that some books have two versions: one is regular, and the other one is unabridged. This has a tendency to make the data repetitive, and adds some complexity to the analysis of the data.  

### First Trends Over Time Chart

The first chart compares the difference between the total checkouts of two books, "Mrs. Dalloway" and "The Years". The two lines in the first chart represents two trends of the total checkouts of two books from 2022 to 2023. By looking at this chart, we can clearly see how the popularity of each book varies as time goes by. For example, we can notice that the general popularity of "Mrs. Dalloway" is higher than that of "The Years", ranging from *20* to *40*. However, the popularity of "The Years" suddenly peaks at *42* in October 2022, which is the highest number of the total checkout in this chart. 

``````{r, echo = FALSE, warning = FALSE, message = FALSE, code = readLines("Chart 1.R")}
```

### Second Trends Over Time Chart

The second chart clearly shows how the total checkouts of each material type vary over time. By looking at this chart, we can see that the regprint is the least popular material type from 2022 to 2023, ranging from *100* to *300*. Generally speaking, the ebook and the audiobook are the most favored by people in Seattle. In January 2023, the total checkout of the audiobook reaches *21932*, which is the maximum amount of the total checkout in the second chart. 

``````{r, echo = FALSE, warning = FALSE, message = FALSE, code = readLines("Chart 2.R")}
```

### Your Choice

The third chart is a stacked bar chart, which is able to demonstrate the total checkouts of all 12 months in 2022 based on the usage class. Generally speaking, people prefer to use digital books rather than physical books in 2022. In August, the total checkout of digital books reaches its maximum at *416682*; while in January, the total checkout of physical books peaks at *339344*. Overall, there is no huge difference between the total checkout of each month, with January and August slightly higher. 

``````{r, echo = FALSE, warning = FALSE, message = FALSE, code = readLines("Chart 3.R")}
```


