---
title: "A3: SPL Library Checkouts"
output: html_document
---

### Introduction

An introduction of the data and a description of the trends/books/items you are choosing to analyze (and why!)

### Summary Information

Write a summary paragraph of findings that includes the 5 values calculated from your summary information R script

These will likely be calculated using your DPLYR skills, answering questions such as:

- What is the average number of checkouts for each item?
- What is the month or year with the most/least checkouts for a book that you're interested in?
- What is the month or year with the most/least checkouts for ebooks?
- How has the number of print book checkouts changed over time?

Feel free to calculate and report values that you find relevant.

### The Dataset

- Who collected/published the data?  
- What are the parameters of the data (dates, number of checkouts, kinds of books, etc.)?
- How was the data collected or generated?  
- Why was the data collected?  
- What, if any, ethical questions do you need to consider when working with this data?  
- What are possible limitations or problems with this data?   (at least 200 words)


### First Trends Over Time Chart

The first chart compares the difference between the total checkouts of two books, "Mrs. Dalloway" and "The Years". The two lines in the first chart represents two trends of the total checkouts of two books from 2022 to 2023. By looking at this chart, we can clearly see how the popularity of each book varies as time goes by. For example, we can notice that the general popularity of "Mrs. Dalloway" is higher than that of "The Years", ranging from *20* to *40*. However, the popularity of "The Years" suddenly peaks at *42* in October 2022, which is the highest number of the total checkout in this chart. 

``````{r, echo = FALSE, warning = FALSE, message = FALSE, code = readLines("Chart 1.R")}
```

### Second Trends Over Time Chart

The second chart clearly shows how the total checkouts of each material type vary over time. By looking at this chart, we can see that the regprint is the least popular material type from 2022 to 2023, ranging from *100* to *300*. Generally speaking, the ebook and the audiobook are the most favored by people in Seattle. In January 2023, the total checkout of the audiobook reaches *21932*, which is the maximum amount of the total checkout in the second chart. 

``````{r, echo = FALSE, warning = FALSE, message = FALSE, code = readLines("Chart 2.R")}
```

### Your Choice


``````{r, echo = FALSE, code = readLines("chart2_example.R")}
```


